Racial and Ethnic Differences in ETI: Outcomes

### 2024-08-05 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti_outcomes.qmd
make ETI outcomes dataset on Lambda

```{r setup}
#| include: false
# Libraries
library(tidyverse)
library(gtsummary)
library(ggflowchart)
library(lmerTest)
library(splines)
library(ggeffects)
# Paths
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/tim/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

Continuous variables were averaged across all years for each person, and categorical variables are reported as the most common value.

@@

```{r results='asis'}
#| message: false
invisible(lapply(continuous_outcomes, function(o) {
  # Formula
  f <-
    as.formula(paste0(
      o,
      "~ bs(Days, knots = 0, degree = 1) * Race + (1 | eDWID)"
    ))
  m <- lmer(f, data = encounter)
  # Print table
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  cat("### Model results")
  cat("\n")
  cat("\n")
  m %>%
    tbl_regression() %>%
    print()
  cat("\n")
  cat("\n")
  # Plot
  cat("\n")
  cat("\n")
  cat("## Model predictions")
  cat("\n")
  cat("\n")
  pred <- predict_response(m, terms = c("Days[-1095,0,730]", "Race"))
  pred %>% gt()
  cat("\n")
  cat("\n")
  cat("### Plot")
  cat("\n")
  cat("\n")
  pred %>%
    plot() %>%
    print()
  cat("\n")
  cat("\n")
}))
```

>>>>

```{r setup}
#| include: false
# Libraries
library(tidyverse)
library(gt)
library(gtsummary)
library(ggflowchart)
library(lmerTest)
library(splines)
library(ggeffects)
# Paths
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/timvigers//OneDrive/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

Continuous variables are reported at the most recent visit prior to ETI start for each person, and categorical variables are reported as the most common value.

@@

```{r results='asis'}
#| message: false
invisible(lapply(continuous_outcomes[1:3], function(o) {
  # Formula
  f <-
    as.formula(paste0(
      o,
      "~ bs(Days, knots = 0, degree = 1) * Race + (1 | eDWID)"
    ))
  m <- lmer(f, data = encounter)
  # Print table
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  cat("### Model results")
  cat("\n")
  cat("\n")
  m %>%
    tbl_regression() %>%
    print()
  cat("\n")
  cat("\n")
  # Plot
  cat("\n")
  cat("\n")
  cat("## Model predictions")
  cat("\n")
  cat("\n")
  pred <- predict_response(m, terms = c("Days[-1095,0,730]", "Race"))
  pred %>% print()
  cat("\n")
  cat("\n")
  cat("### Plot")
  cat("\n")
  cat("\n")
  pred %>%
    plot() %>%
    print()
  cat("\n")
  cat("\n")
}))
```
